---
title: "Replication of Your Understanding is My Understanding by Sloman & Rabb (2016, Psychological Science)"
author: "Lawrence Liu (hrlarry@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

##Introduction

<!-- [No abstract is needed.]  Each replication project will have a straightforward, no frills report of the study and results.  These reports will be publicly available as supplementary material for the aggregate report(s) of the project as a whole.  Also, to maximize project integrity, the intro and methods will be written and critiqued in advance of data collection.  Introductions can be just 1-2 paragraphs clarifying the main idea of the original study, the target finding for replication, and any other essential information.  It will NOT have a literature review -- that is in the original publication. You can write both the introduction and the methods in past tense.   -->

The original paper can be found here: 

##Methods

###Power Analysis

<!-- Original effect size, power analysis for samples to achieve 80%, 90%, 95% power to detect that effect size.  Considerations of feasibility for selecting planned sample size. -->

Power analysis pending due to confusion/potential error in original paper about the analysis performed.

###Planned Sample

<!-- Planned sample size and/or termination rule, sampling frame, known demographics if any, preselection rules if any. -->

We are planning on recruiting 365 US residents from Amazon's Mechanical Turk. This is equivalent to 2.5x the sample size of the original study.

###Materials

<!-- All materials - can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article. -->

This replication reuses the open materials on the original article's OSF posting, which can be found here: https://osf.io/24kvu/

###Procedure	

<!-- Can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article. -->

From the original article:

"One hundred forty-six U.S. residents (56% female, 44% male; mean age = 33.9 years) were recruited using Amazon's Mechanical Turk, screened for participation in the previous experiment, and given a small payment. Sample size was chosen to satisfy counterbalancing schemes and was in keeping with related prior research. Participants received the same instructions as in Experiment 1, except for one modification: The cover story claimed that the study concerned recent scientific discoveries "made by DARPA, the research agency of the U.S. military," an entity chosen for its power to keep scientific knowledge absolutely secret. Participants rated their understanding of six fictional natural phenomena (an example is shown in Table 1). Each participant read two descriptions of phenomena that had been thoroughly explained by the discovering scientists in a published article (public CK condition); two descriptions of different phenomena that had not yet been explained but that had been described in a published article by the scientists who discovered it (public no-CK condition); and two descriptions of still other phenomena that had been thoroughly explained but only in classified documents (secret CK condition). The descriptions contained no causal or explanatory information. Items were counterbalanced across conditions and across two random presentation orders. For reasons unrelated to our current purposes, each participant then generated a step-by-step causal explanation for two of the phenomena and rerated understanding of the two items. They also answered a question incorporated as an attention check and were asked if they had consulted external Web sites during the experiment.""

###Analysis Plan

<!-- Can also quote directly, though it is less often spelled out effectively for an analysis strategy section.  The key is to report an analysis strategy that is as close to the original - data cleaning rules, data exclusion rules, covariates, etc. - as possible.   -->

<!-- **Clarify key analysis of interest here**  You can also pre-specify additional analyses you plan to do. -->

As stated in the original paper, we will use a repeated measures ANOVA on the log-transformed ratings of understanding. However, it appears that the report statistic in the original paper comes from a mixed effects linear model on the log-transformed ratings of understanding, which we will also use. Finally, the original paper doesn't appear to adequately justify the use of the log-transformed ratings, so we will use the absolute ratings with the same models. Furthermore, we will see if there is a linear order effect based on the presentation order of the phenomena.

Additional, we have added a manipulation check that was not used in the original study. We will exclude any participant who has more than 1 error (false positive or false negative) in identifying the different fictitious phenomena used in the study. We will continue to exclude participants who fail the attention check or claim to have used outside resources (see Materials).

###Differences from Original Study

<!-- Explicitly describe known differences in sample, setting, procedure, and analysis plan from original study.  The goal, of course, is to minimize those differences, but differences will inevitably occur.  Also, note whether such differences are anticipated to make a difference based on claims in the original article or subsequent published research on the conditions for obtaining the effect. -->

Key differences in this replication are:
-A larger sample consisting of 365 participants
-A different counterbalancing scheme. Counterbalancing still exists across conditions (for 6 permutations of presentation order of the 3 conditions), but the order of the phenomena is a true random presentation (as opposed to randomly picked from a limited set of sequences for a pseudo-random order)
-Different analyses: in addition to replicating the model in the original paper using log-transformed data, we will run the same model on the absolute data and also additionally run a mixed effect model.

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.

#### Actual Sample
  Sample size, demographics, data exclusions based on rules spelled out in analysis plan

#### Differences from pre-data collection methods plan
  Any differences from what was described as the original plan, or “none”.


##Results


### Data preparation

Data preparation following the analysis plan.
	
```{r include=FALSE}
#Load in relevant libraries and functions
library(tidyverse)
library(stringr)
library(lme4)
```


```{r include=F}
####Setting some parameters
NUM_CONDITIONS = 3
NUM_PHENOMENA = 6
NUM_SCENARIOS_PER_SUBJECT = 6

####Import data
df_raw <- read_csv(file = "data/pilotA.csv")
instructions_colnum <- which(colnames(df_raw) == "Instructions")
problem_text <- df_raw[1,(instructions_colnum+1):(instructions_colnum+(NUM_CONDITIONS * NUM_PHENOMENA * NUM_SCENARIOS_PER_SUBJECT))]

####Update column names using the question text

#For loop to determine the new name
for(i in 1:(NUM_CONDITIONS * NUM_PHENOMENA * NUM_SCENARIOS_PER_SUBJECT)){
  #Extract which scenario number (as seen by the participant) this particular question text was for
  scenario_num <- as.integer((i-1)/18) + 1
  
  #Extract which condition this particular question text contained
  condition <- if((i-1)%%18 < 6) "secret_cok" else if((i-1)%%18 < 12) "public_cok" else "public_noncok"
  
  #Extract which phenomenon this particular question text contained
  phenomenon <- str_extract(as.character(problem_text[1,i]),"(rock)|(fish)|(ice)|(weather)|(sand)|(wood)")
  
  #Store all of this information
  problem_text[2,i] <- scenario_num
  problem_text[3,i] <- condition # e.g. "public_cok"
  problem_text[4,i] <- if(phenomenon == "rock") "glowing_rock" else
    if(phenomenon == "fish") "flying_fish" else 
    if(phenomenon == "ice") "warm_ice" else
    if(phenomenon == "weather") "liquid_helium" else
    if(phenomenon == "sand") "self_forming_glass" else "reflective_smoke"
  problem_text[5,i] <- paste(problem_text[2,i], problem_text[3,i], problem_text[4,i], sep="~")
}

#Update column name in df_raw
names(df_raw)[(instructions_colnum+1):(instructions_colnum+(NUM_CONDITIONS * NUM_PHENOMENA * NUM_SCENARIOS_PER_SUBJECT))] <- problem_text[5,]

####Remove question text row and convert raw data into long form
df_long <- df_raw %>%
  filter(row_number()!=1) %>% #Remove the secondary headers
  mutate(subject_id = 1:n()) %>% #Add subject IDs
  gather("order:condition~phenomenon", "rating", `1~secret_cok~glowing_rock`:`6~public_noncok~reflective_smoke`, na.rm = TRUE) %>%
  separate("order:condition~phenomenon", 
           into = c("order","condition", "phenomenon"), 
           sep = "~")  %>%
  mutate_each(funs(as.integer(ifelse(is.na(.),0,.), na.rm=TRUE)), contains("Manipulation Check")) %>% #Change all manipulation check cells to integers
  mutate(`Attention Check` = as.integer(ifelse(is.na(`Attention Check`),0,`Attention Check`), na.rm=TRUE)) %>% #Change all attention check cells to integers
  mutate(rating = as.integer(rating, na.rm=TRUE)) #Change all ratings to integers

#### Data exclusion / filtering
df_long <- df_long %>%
  filter(`Attention Check` == 16) %>% #Must pass attention check
  mutate("Manipulation Check Errors" = (1 - `Manipulation Check_1`) + (1 - `Manipulation Check_2`) + #False negatives
           (1 - `Manipulation Check_3`) + (1 - `Manipulation Check_4`) + #False negatives
           (1 - `Manipulation Check_5`) + (1 - `Manipulation Check_6`) + #False negatives
           `Manipulation Check_7` + `Manipulation Check_8` + `Manipulation Check_9`) %>% #False positives
  filter(`Manipulation Check Errors` <= 1)

df_long
```

### Confirmatory analysis

The analyses as specified in the analysis plan.  

```{r}
#Recreate Table 2 from original paper
df_long %>% 
  group_by(condition) %>%
  summarise(mean = mean(rating), sd = sd(rating))

```

```{r}
#Recreate statistics that the original paper created
test <- df_long %>%
  group_by(subject_id, condition) %>%
  summarise(mean = mean(rating)) %>%
  mutate(Log_Understanding = log(mean))

model_rep <- lmer(Log_Understanding ~ condition + (1 | subject_id), data=test) #Original model done in the study replicated
model <-  lmer(Log_Understanding ~ 1 + (1 | subject_id), data=test)

anova(model_rep) 
anova(model,model_rep)
summary(model_rep) #Original F-statistic reported from here
```

```{r}
#Original paper claimed to have used a repeated measures anova
model_aov <- aov(Log_Understanding ~ condition + Error(subject_id/condition), data=test)
summary(model_aov)
```

```{r}
#Original paper also performed a t-test between the conditions
public_cok <- test %>%
  filter(condition == "public_cok")

public_noncok <- test %>%
  filter(condition == "public_noncok")

secret_cok <- test %>%
  filter(condition == "secret_cok")

t.test(as.matrix(public_noncok[,"Log_Understanding"]), as.matrix(public_cok[,"Log_Understanding"]), var.equal = TRUE, paired=TRUE)
t.test(as.matrix(secret_cok[,"Log_Understanding"]), as.matrix(public_cok[,"Log_Understanding"]), var.equal = TRUE, paired=TRUE)
t.test(as.matrix(public_noncok[,"Log_Understanding"]), as.matrix(secret_cok[,"Log_Understanding"]), var.equal = TRUE, paired=TRUE)

```

*Side-by-side graph with original graph is ideal here*

###Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
